A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

No que diz respeito à simulação das ações executadas por jogadores cujos avatares estão situados em regiões diferentes, deve-se decidir como será feita a simulação. Como o foco deste trabalho não é a simulação em si, mas sim a otimização do uso de largura de banda através de um novo algoritmo de gerenciamento de interesse, decidiu-se que a simulação será realizada pelo servidor ao qual o cliente daquele jogador está conectado. Dessa forma, se o jogador cujo avatar está em $R_i$ executar uma ação próximo à fronteira, envolvendo entidades em $R_j$, será o servidor $S_i$ quem decidirá o resultado destas ações, repassando a $S_j$ apenas o novo estado já calculado.

>>>>

Regarding the simulation of the actions performed by players whose avatars are located in different regions, it must be decided how it will be performed. As the focus of this work is not the simulation itself, but the bandwidth usage optimization through a new interest management algorithm, it was decided that the simulation will be performed by the server to which the client of that player is connected. Thus, if the player whose avatar is in region $R_i$ performs an action near the border involving entities in $R_j$, it is the server $S_i$ who will decide the outcome of these actions, forwarding only the already calculated new state to $S_j$.

This way, the details of this mechanism will not result in relevant changes to the interest management. When a player $J$, whose avatar is near the border of a region, performs actions which resultos
